Titeln på avhandlingens språk

### 2023-05-19 body/part1/chapter2-relatedwork/key_contributions.tex
edge computing

\Cref{paper:olguinmunoz2022cleave} extends my methodology to the study of control systems for \glspl{NCS} on Edge Computing.
These applications are similarly difficult to benchmark as \gls{WCA}, particularly at scale on multi-tenant systems, due to their client-side complexity and extreme sensitivity to latency.
To address these challenges, my co-authors and I introduce yet another tool, \gls{CLEAVE}, for the emulation and subsequent deployment of these systems on edge computing infrastructure.
\gls{CLEAVE} allows us both to emulate the physical components of a relatively simple control system plant and deploy real algorithms for its control.
The middleware software abstracts away the network from the development of these workloads, enabling quick prototyping and deployment.
We then present use-case scenarios demonstrating the scalability and flexibility of their approach by deploying scenarios with a large number of loops without the need for domain-specific hardware.

@@

Next, in \cref{paper:olguinmunoz2023realistic} my co-authors and I introduce the first ever data-driven model of human timings for \gls{WCA}, built upon the data and insights collected for \cref{paper:olguinmunoz2021impact}.
The model is validated against previously obtained results, both through simulated, controlled executions and deployments on a real edge computing testbed.
The paper goes on to explore potential implications of this model for \gls{WCA} system optimization potential, particularly in the domains of energy consumption and sampling strategies.

>>>>

\Cref{paper:olguinmunoz2022cleave} extends my methodology to the study of control systems for \glspl{NCS} on Edge Computing.
These applications are similarly difficult to benchmark as \gls{WCA}, particularly at scale on multi-tenant systems, due to their client-side complexity and extreme sensitivity to latency.
To address these challenges, my co-authors and I introduce yet another tool, \gls{CLEAVE}, for the emulation and subsequent deployment of these systems on Edge Computing infrastructure.
\gls{CLEAVE} allows us both to emulate the physical components of a relatively simple control system plant and deploy real algorithms for its control.
The middleware software abstracts away the network from the development of these workloads, enabling quick prototyping and deployment.
We then present use-case scenarios demonstrating the scalability and flexibility of their approach by deploying scenarios with a large number of loops without the need for domain-specific hardware.

@@

Next, in \cref{paper:olguinmunoz2023realistic} my co-authors and I introduce the first ever data-driven model of human timings for \gls{WCA}, built upon the data and insights collected for \cref{paper:olguinmunoz2021impact}.
The model is validated against previously obtained results, both through simulated, controlled executions and deployments on a real Edge Computing testbed.
The paper goes on to explore potential implications of this model for \gls{WCA} system optimization potential, particularly in the domains of energy consumption and sampling strategies.

### 2023-05-19 body/part1/chapter3-contributions/wca-implications.tex
edge computing

This new model is based on the comprehensive study of human behavior in the presence of feedback latency outlined in \cref{paper:olguinmunoz2021impact}, and has significant implications for the optimization of edge computing systems.
By incorporating a more accurate representation of human behavior into the methodology, the impact of system design choices on the end-user experience can better be assessed.
This, in turn, enables future research into optimization strategies that are more effective at improving the overall quality of service for edge computing applications.

@@

Overall, this case study highlights the potential benefits of using my methodology coupled with a realistic model of human timing behavior in edge computing systems.
By considering higher order effects on execution times, such as the impact of neuroticism, the accuracy of predictions can be improved and system performance can be optimized.
However, it is important to note that the effects of using a realistic model may vary depending on the specific context and task being performed.
Further research is needed to explore the generalizability of these findings and to investigate other factors that may impact task completion times in edge computing systems.

>>>>

This new model is based on the comprehensive study of human behavior in the presence of feedback latency outlined in \cref{paper:olguinmunoz2021impact}, and has significant implications for the optimization of Edge Computing systems.
By incorporating a more accurate representation of human behavior into the methodology, the impact of system design choices on the end-user experience can better be assessed.
This, in turn, enables future research into optimization strategies that are more effective at improving the overall quality of service for Edge Computing applications.

@@

Overall, this case study highlights the potential benefits of using my methodology coupled with a realistic model of human timing behavior in Edge Computing systems.
By considering higher order effects on execution times, such as the impact of neuroticism, the accuracy of predictions can be improved and system performance can be optimized.
However, it is important to note that the effects of using a realistic model may vary depending on the specific context and task being performed.
Further research is needed to explore the generalizability of these findings and to investigate other factors that may impact task completion times in Edge Computing systems.

### 2023-05-19 body/part1/chapter4-conclusions/conclusions.tex
edge computing

Finally, I see tremendous opportunities for testbed-driven research in Edge Computing.
My current efforts in this context aim towards the extension of our Ainur framework and its integration with \gls{CHI}~\cite{keahey2020lessons}.
I believe Ainur's unique focus on fully-automated end-to-end wireless edge computing experimentation makes it valuable addition to the \gls{CHI} stack.
At the same time, integrating with \gls{CHI} will provide a number of features and functionalities which will greatly expand Ainurs potential, such as resource reservation, multi-tenant testbed access, and automated bare-metal and \gls{VM}-host instantiation.

>>>>

Finally, I see tremendous opportunities for testbed-driven research in Edge Computing.
My current efforts in this context aim towards the extension of our Ainur framework and its integration with \gls{CHI}~\cite{keahey2020lessons}.
I believe Ainur's unique focus on fully-automated end-to-end wireless Edge Computing experimentation makes it valuable addition to the \gls{CHI} stack.
At the same time, integrating with \gls{CHI} will provide a number of features and functionalities which will greatly expand Ainurs potential, such as resource reservation, multi-tenant testbed access, and automated bare-metal and \gls{VM}-host instantiation.
